---
title: "For Loops, Conditionals and Functions"
author: "J.Blondeau"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This week you will get some practice with 'for loops' and then get introduced to creating your own functions.  


### For loops

Next set of questions will all use for loops to solve.

1.  Create a for loop that prints each integer from 1 to 25

2.  Create a for loop that prints all the unique species from the 'fish_psu_density' dataset

3.  Create a for loop that prints the square of each integer from 1 to 10

4.  Create a for loop that prints **only** the odd numbers from a sequence of integers from 1 to 20

5.  Create a for loop that prints integer 'is even' or 'is odd' for a sequence of integers from 1 to 10

***
    "1 is odd"
    "2 is even"
    ...
***

6.  Create a for loop that inserts all the unique species from 'fish_psu_density' into a new vector 

***
hint:
```{r, eval=FALSE}
a <- c()
for (variable in sequence) {
  insert variable into vector 'a'
}
```
***

### Creating functions

7.  Create a function that squares any given value

8.  Create a function that calculates the circumference and area of a circle given any radius

9.  Create a function that returns the number of samples per YEAR and STRAT from the 'fish_psu_density' dataframe

10.  Create a function that returns a point and line plot (+- standard error) of mean density over time by REGION for any species.  Use the 'fish_psu_density' dataset.
      - $standard \  error =  \frac{standard\ deviation}{\sqrt{sample\ size}}$
      - edit the ggplot parameters for a cleaner look
      - the title of the plot should be dynamic, displaying the common name of the fish chosen
